{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-06-01 bmvc_review.tex
Revised the text.

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry other
sensors than a lightweight or an array of monocular cameras. For
example, instead of having just bare flight function with video
recording, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. Specifically, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
$300$-$400$ fps so that it could run, at least, faster than 30 fps
when it is deployed on a low-end, embedded system.\footnote{In
  general, it would be very hard to compare an Intel or AMD processor
  running on a desktop or a laptop with that, e.g., ARM, of a
  single-board, embedded system in terms of run-time performance of a
  computer vision algorithm. This is primarily because of difference
  in their architectures. But we empirically found this computation
  useful and reasonable based on specific processors, e.g., Intel's i7
  quad-core vs ARM Cortex A53 -- the computation about an 1/10th scale
  down of computational resources from a typical PC to an embedded
  system.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can be easily implemented and run very efficiently
on the fly. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time primarily \cite{henriques2015high}. This is
primarily due to the dilemma of stability-plasticity in updating
appearance model, where the appearance model will be overfitted to
only the images used to train, unless a compromise on the frequency of
updating the model is carefully implemented
\cite{santner2010prost}. For example, one may handle a target's scale
variation by just concatenating multiple correlation filters including
KCF and running them on each frame. Alternatively one could think of
scanning the region of interest (ROI) with a list of templates in
predefined scale ratios to find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence to figure out the scale of a target. This is based on an
assumption that the scale of a target would not change much over two
consecutive frames. Similarly \cite{ma2015long} used two KCFs to learn
the translation and scale of a target separately. To be more specific,
a KCF is used to learn the translation of the target and its
background. Given this, another KCF is used to learn the target area
to estimate a new scale of the target. However, because of running
more than a KCF on each frame, this method degrades its run-time
performance (i.e., $\leq 50 fps$). Our method is motivated by this
idea -- the idea of deploying multiple KCFs to address the issues of
single target tracking: scale and translation, but in a more efficient
way. In particular, we use an ensemble of KCFs in turn, instead of
running them all together on every frame. We deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, we could still address the scale change
and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{fig:Filters} shows
examples of the region of interest (ROI) associated with $R_{t}^{S}$,
$R_{t}^{L}$, and $R_{s}$. Figure \ref{Workflows} illustrates the
work-flow of the {\it E}nKCF.
\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
\end{tabular}
\caption{The workflow of {\it E}nKCF tracking algorithm. We show the
  first seven frames of tracking where the first frame is the
  initialization frame. Afterward, the order of deploying three KCFs
  is repeating.}
\label{Workflows}
\end{figure}
The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps. In particular,
the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCFs, in
turn, to more effectively address the scale variance and the dynamic
maneuver of a target while preserving run-time performance as high as
possible. To minimize any potential performance gap from transiting
one KCF to another, we use a Bayes filter.

@@

{\it Burak: Please remove the in-figure text ``Correlation Filters
  employed...'' from Figure 3. Can you make the examples of these
  filters using the picture of ``David'' shown at Figure 2.}

{\it YoungWoo : I just did it. Let me know if you see any problem with it.}

>>>>

%%%%%%%%% BODY TEXT
\section{Introduction}
A recent advancement of air/ground/water unmanned vehicle technologies
has increased interests on deploying intelligent algorithms to
existing embedded and mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because payloads of those mobile platforms are limited to carry other
sensors than a lightweight or an array of monocular cameras. For
example, instead of just flying to record a video based on manual
commands, an unmanned air vehicle (UAV) equipped with an object or
feature following functionality would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking algorithm aiming at
running on any embedded or mobile platforms that doesn't require an
offline training. Specifically, we would like to make our algorithm 1)
learn the appearance model of a target on the fly and 2) run as fast
on a typical desktop as up to $300-400$ fps so that it could run, at
least, faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would be very hard to compare an Intel
  or AMD processor running on a desktop or a laptop with that, e.g.,
  ARM, of a single-board, embedded system in terms of run-time
  performance of a computer vision algorithm. This is primarily
  because of difference in their architectures. But we empirically
  found this computation useful and reasonable based on specific
  processors, e.g., Intel's i7 quad-core vs ARM Cortex A53 -- the
  computation about an 1/10th scale down of computational resources
  from a typical PC to an embedded system.}

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that a target location is given at the beginning
like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, this
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter offers a less complex
solution, $\mathcal{O}(n\log n)$ over element-wise multiplication in a
frequency domain \cite{bolme2010visual,henriques2015high}. Thank to
this reformulation, an object tracking pipeline based on the
correlation filter can run very efficiently and be even easily
implemented. In fact, an extension of a linear correlation filter, the
kernelized correlation filter with multi-channel features
\cite{henriques2015high} showed impressive object tracking results and
outperformed other state-of-the-art tracking algorithms in terms of
run-time and tracking accuracy. However, a vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time \cite{henriques2015high}. This is primarily due to
the dilemma of stability-plasticity in updating appearance model,
where the appearance model will be overfitted to only the images used
to train, unless a compromise on the frequency of updating the model
is carefully implemented \cite{santner2010prost}. For example, one may
handle a target's scale variation by just concatenating multiple
correlation filters including KCF and running them on each
frame. Alternatively one could think of scanning the region of
interest (ROI) with a list of templates in predefined scale ratios to
find the target in appropriate scale
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
these approaches will drastically reduce run-time performance because
they are proposed to run multiple of a correlation filter including
KCF on each frame.

@@

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and estimate a correct scale afterward. In
particular, Zhang and his colleagues use the MOSSE tracker to estimate
a target's translation. And then they attempted to update the scale of
the target by further analyzing image, sub-regions with high
confidence to figure out the scale of a target. This is based on an
assumption that the scale of a target would not change much over two
consecutive frames. Similarly, Ma and his colleagues used two KCFs to
learn the translation and scale of a target separately
\cite{ma2015long}. In particular, a KCF is used to learn the
translation of the target and its background. Given this, another KCF
is used to learn the target area to estimate a new scale of the
target. However, because of running more than a KCF on each frame,
this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. In particular, we use an
ensemble of KCFs in turn, instead of running them all together on
every frame. We deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, we could address the scale change and
estimate target's motion efficiently while maintaining or increasing
run-time performance. Figure \ref{fig:Filters} shows examples of the
region of interest (ROI) associated with $R_{t}^{S}$, $R_{t}^{L}$, and
$R_{s}$. Figure \ref{Workflows} illustrates the work-flow of the {\it
  E}nKCF.
\begin{figure}[!t]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=12.00cm]{./figures//Workflow_MKCF+PF.pdf}}\\
\end{tabular}
\caption{The workflow of {\it E}nKCF tracking algorithm. We show the
  first seven frames of tracking where the first frame is the
  initialization frame. Afterward, the order of deploying three KCFs
  is repeating.}
\label{Workflows}
\end{figure}
The contribution of this study is a novel, single-target tracking
algorithm running in a very high-speed, $\geq 300$ fps. In particular,
the proposed algorithm, {\it E}nKCF, deploys an ensemble of KCFs, in
turn, to more effectively address the scale variance and the dynamic
maneuver of a target while preserving run-time performance as high as
possible. To minimize any potential performance gap from transiting
one KCF to another, we use a Bayes filter.

@@
